\section{Project Management}
\subsection{Project Plan}
The problem can be broken down into a number of key elements, each of which can be assigned to an individual or a group depending on the difficulty.
The project was broken into the following elements:
\begin{itemize}
    \item \textbf{Web application} A web application consisting of a front end and a back end to facilitate communication and control between the rover and the user.
    \item \textbf{Control system} A control system to balance the rover and drive the motors for a given movement.
    \item \textbf{Computer vision} A computer vision system to outline the maze and locate the rover based on the detection of beacons placed in known position around the maze.
    \item \textbf{Navigation and routing} A navigation and routing algorithm to control the path of the rover ensuring it does not collide with walls and navigates through the maze.
    \item \textbf{Power delivery} A power delivery system for the LED beacons.
\end{itemize}

These key components were designed with scalability and adaptability in mind so that while they were developed independently, they could be connected to complete the design. For example, the web API can handle multiple rovers with different IDs.

\subsection{Milestones}
Several milestones were met in the development of the project, 
the progression through these milestones were used to keep track of the progress 
of the project and to identify areas that needed more attention. 
The progress was projected with a Gantt chart.

The key milestones that were achieved are as follows:
\begin{itemize}
    \item The completion and testing of the back-end API.
    \item The completion and integration of the front-end interface.
    \item The integration of the MPU6050 with the ESP32 and to the back-end API.
    \item Expanding the vision system to locate other colours of beacon.
    \item A communication channel between the FPGA and the ESP32.
    \item Motor driver and control system integration.
    \item The completion of the power delivery system.
\end{itemize}


\subsection{Meetings and Organisation}
Team meetings were held on Microsoft Teams to keep each other up to date. 
In these meetings the progress on each subsystem were discussed 
and then an overall discussion on the integration of the subsystems.